Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-02-05 man/figures/ring_climate.Rmd
update figures and chronos
add tick marks

```{r plot_tmax}
p_tmax <- df %>% filter(v_name == 'T max') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'bottom') + 
  ylab('Correlation') + 
  annotate("text", x = 2, y = 0.35, label = "T max", fontface =2, size = 3.5)
```

```{r plot_tmin}
p_tmin <- df %>% filter(v_name == 'T min') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.35, label = "T min", fontface =2, size = 3.5)
```

@@

p_prec_spei <- dfprec_spei %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  geom_vline(xintercept=20) +
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.2, 0.8), 
                     breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8)) +
  scale_x_continuous(breaks = labelitas$id, labels = labelitas$month_name, position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.75, label = "Prec", fontface =2, size = 3.5) + 
  annotate("text", x = 23, y = 0.75, label = "SPEI", fontface =2, size = 3.5)
```

@@

```{r plot_out, fig.height=6, dpi = 300, out.width = 0.8} 
ring_climate
```

>>>>

```{r plot_tmax}
p_tmax <- df %>% filter(v_name == 'T max') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'bottom') + 
  ylab('Correlation') + 
  annotate("text", x = 2, y = 0.35, label = "T max", fontface =2, size = 3.5)
```

```{r plot_tmin}
p_tmin <- df %>% filter(v_name == 'T min') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.35, label = "T min", fontface =2, size = 3.5)
```

@@

p_prec_spei <- dfprec_spei %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  geom_vline(xintercept=20) +
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.2, 0.8), 
                     breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8), 
                     sec.axis = dup_axis(name = NULL)) +
  scale_x_continuous(breaks = labelitas$id, labels = labelitas$month_name, position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.75, label = "Prec", fontface =2, size = 3.5) + 
  annotate("text", x = 23, y = 0.75, label = "SPEI", fontface =2, size = 3.5)
```

@@

```{r plot_out, fig.height=5, dpi = 300, out.width = 0.8} 
ring_climate
```
